The paper on \Large \bf Blockchain Frontrunning

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] edits till section 5

As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not limited to the financial markets. Front-running can also occur within other (non-financial) blockchain applications such as naming systems. Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduces single point of failures in the entire web. Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names. These domains which can be resolved using any Ethereum web3 compatible browser. Although a sealed auction (\textit{startAuctionsAndBid()}) is used in ENS implementation, the deposit should be equal or bigger than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to over bid the initial sealed bid. By doing so the front-runner invalidates the original bid and hence registers the domain name himself. Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.  In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool to be mined by Ethereum miners in a block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}. Front-running practice can happen in the traditional domain name system (DNS) as well. Domain name registrars can steal available domain names once seeing a query from users that looks up that domain's availability. In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.
%______________________________________________________________%
\subsection{Crypto-Collectibles Games.}

Crypto-Collectibles, also known as ERC-721 Non-Fungible Token Standard~\cite{erc721}, are one of the applications of Ethereum blockchain. Cryptokitties is known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}. Their market cap reached more than 6 million dollars in the first months their launch. Crypto-Collectibles, are similar to ERC-20 tokens and can be listed on exchanges. Most of the front-running issues applied to the exchanges also apply to DApps using ERC-721 tokens. \\

As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. See Figure~\ref{fig:cryptokittie}.
To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract. This is similar to open auctions, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder. 
% https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40

%Possibly remove this figure due to page limit
\begin{figure}[h]
\centering
\includegraphics[width=0.4\linewidth]{figures/cryptokittie842912.png}
\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
\end{figure}

@@

Due to deterministic nature of blockchains, running gambling games based on randomness is close to impossible. There had been attempts to use block headers or such as the seed to randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run, thus prone to front-running and miner's manipulation. Many infamous gambling games are now running on Ethereum network and front-running them requires a level of sophistication and knowledge of the internal of the games and Ethereum.\\
One of the most popular smart contracts on Ethereum blockchain belongs to a controversial gambling game named \texttt{Fomo3d}, also known as \textit{Exit Scam}\footnote{\url{https://exitscam.me/play}}. The aim of this game is to be the last person purchasing the key when the time goes to zero in which every ticket purchase increases the timer by 30 seconds. It was believed that because of the nature of the game, it will never end, however on August 22, 2018 the first round of the game ended and the winner took 10,469 Ether\footnote{First winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}}, equivalent to 2.1 Million dollars on the time of writing. 
It is believed that the winner, used a sophisticated approach to finish last~\cite{fomo3dhacker}, we call this approach \textit{Denial-of-service Front-running}. The winner deployed a few high gas consumption smart contracts prior to the win, when the timer of the game reached about 3 minutes, the winner bought 1 ticket and sent multiple high gasPrice transactions to aforementioned smart contracts to lure the miners to mine these highly profitable transactions. For a DoS front-running to work, attacker floods the network with high gasPrice transactions to prevent other transactions to go through. Luckily enough the winner was able to congest the network in a way that no other ticket purchases were mined in the 3 minutes window and the miners were prioritizing the high gasPriced transactions over other transactions. All the details mentioned here are drawn from the transaction history on the blockchain and unless otherwise proven seem to be the way the winner acted to win the pot. 
%probably needs more work to be good enough. more resources will be out in the coming days !

>>>>

Front-running can also occur within non-financial blockchain applications such as naming systems. Recently, many blockchain-based domain registrars have been designed and implemented to eliminate the role of central parties \ie domain name system (DNS) which itself introduced single point of failures to the entire web. Ethereum Name Service (ENS)\footnote{\url{https://ens.domains/}}, is the most popular decentral naming service that uses a sealed auction to facilitate the procedures of purchasing new \texttt{.eth} domain names. Although sealed auction method is used in ENS implementation, the normal work flow uses \textit{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to out bid the initial sealed bid. By doing so the front-runner invalidates the original bid and hence registers the domain name himself. Ghazal is another Ethereum-based naming system that allows users to register \texttt{.ghazal} domain names and bind certificates to those names~\cite{moosavighazal}.  As Ghazal is using a registration method in plain text, it is susceptible to front-running. 
Note that front-running domain names has been a subject of discussion outside the context of blockchian applications before~\cite{sac022en33:online}. Domain name registrars can steal available domain names upon seeing a query from an interested user for the availability of the domain. In this case, the registrar can register the domain name ahead and sell it back to the user for a higher price.
%______________________________________________________________%
\subsection{Crypto-Collectibles Games.}

Crypto-Collectibles, also known as \textit{ERC-721 Non-Fungible Token Standard}~\cite{erc721}, are one of the applications of Ethereum blockchain. Cryptokitties are known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}. Their market cap reached more than 6 million dollars in the first few months their launch, however declined soon after. Crypto-Collectibles, are similar to ERC-20 tokens and can be listed on exchanges. Most of the front-running issues applied to the exchanges also apply to DApps using ERC-721 tokens. \\

As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. %see Figure~\ref{fig:cryptokittie}.
To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract. This is similar to open auctions, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder. 
% https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40

%Possibly remove this figure due to page limit
\begin{figure}[h]
\centering
\includegraphics[width=0.3\linewidth]{figures/cryptokittie842912.png}
\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
\end{figure}

@@

Due to deterministic nature of blockchains, running gambling games based on randomness is close to impossible. There had been attempts to use block headers or such as the seed to randomness but almost all have failed as every data accessible to the smart contract at the time of execution, is also accessible to other smart contracts and they could predict the output on the run, thus prone to front-running and miner\'s manipulation. Many infamous gambling games are now running on Ethereum network and front-running them requires a level of sophistication and knowledge of the internal of the games and Ethereum.\\
One of the most popular smart contracts on Ethereum blockchain belongs to a controversial gambling game named \texttt{Fomo3d}, also known as \textit{Exit Scam}\footnote{\url{https://exitscam.me/play}}. The aim of this game is to be the last person purchasing the key when the timer goes to zero in which every ticket purchase increases the timer by 30 seconds. It was believed that because of the nature of the game, it will never end, however on August 22, 2018 the first round of the game ended and the winner taking 10,469 Ether\footnote{First winner of Fomo3D, won 10,469 Ether \url{ https://etherscan.io/tx/0xe08a519c03cb0aed0e04b33104112d65fa1d3a48cd3aeab65f047b2abce9d508}}, equivalent to 2.1 Million dollars on the time of writing. 
It is believed that the winner, used a sophisticated approach to finish last~\cite{fomo3dhacker}, we call this approach \textit{Denial-of-service Front-running}. The winner deployed a few high gas consumption smart contracts prior to the win, when the timer of the game reached about 3 minutes, the winner bought 1 ticket and sent multiple high gasPrice transactions to aforementioned smart contracts to lure the miners to mine these highly profitable transactions. For a DoS front-running to work, attacker floods the network with high gasPrice transactions to prevent other transactions to go through. Luckily enough the winner was able to congest the network in a way that no other ticket purchases were mined in the 3 minutes window and the miners were prioritizing the high gasPriced transactions over other transactions. All the details mentioned here are drawn from the transaction history on the blockchain and unless otherwise proven seem to be the way the winner acted to win the pot. 
%probably needs more work to be good enough. more resources will be out in the coming days !
